The imprint of global magma oceans on exoplanet demographics

### 2022-12-10 src/tex/ms.tex
introduce survey simulation module

\subsection{Testing the magma ocean hypothesis with current and planned exoplanet missions}
\todo{Introduce survey simulation(s). PLATO, Cheops, Ariel, LIFE (reach out to team; Hendrik Linz produced a LIFE Technology Overview document)?, Nautilus\\ What are threshold missions that are able to detect this signal? =>X meter working for Y years, or X' meter working for Y' years => conclusion could be that there is interesting science to do with intermediate size telescope.}
In previous steps, we generated a population of synthetic planets that orbit synthetic stars, and we have injected the statistical trend expected from the presence of magma oceans on a fraction of the planets.
Only a subset of these planets would be detectable by a transit survey, and their properties can be probed only with a finite precision.
To test the detectability of a magma ocean signature, we simulated several transit surveys with different designs and strategies and explored their capability to recover the magma ocean trend and constrain its parameters.
We assessed this capability based on two determinants: the likelihood that the mission is able to detect the injected trend, and the precision with which it can constrain the parameters of that trend.

@@

>>>>

\subsection{Testing the magma ocean hypothesis with current and planned exoplanet missions}
\todo{Introduce survey simulation(s). PLATO, Cheops, Ariel, LIFE (reach out to team; Hendrik Linz produced a LIFE Technology Overview document)?, Nautilus\\ What are threshold missions that are able to detect this signal? =>X meter working for Y years, or X' meter working for Y' years => conclusion could be that there is interesting science to do with intermediate size telescope.}
In previous steps, we generated a population of synthetic planets that orbit synthetic stars, and we have injected the statistical trend expected from the presence of magma oceans on a fraction of the planets.
Only a subset of these planets would be detectable by a transit survey, and their properties can be probed only with a finite precision.
To test the detectability of a runaway greenhouse transition, we simulated several transit surveys with different designs and strategies and explored their capability to recover the magma ocean trend and constrain its parameters.
We assessed this capability based on two determinants: the likelihood that the mission is able to detect the injected trend, and the precision with which it can constrain the parameters of that trend.

@@

\subsubsection{Survey simulations}
\begin{note}
The survey module of Bioverse converts the synthetic planet sample into a set of uncertainty-laden measurements of some parameters of a subset of that sample.
   This task includes selection of the targets, application of any detection biases, and conducting simulated measurements.
   All of the above are specific to the particular survey.

Current and near-future missions focusing on Earth-sized planets target several host star spectral types, and their exact sample selection is based on specific mission objectives.
    We thus chose a broad selection function centered on general detectability of transits with state-of-the-art technology.
